### 2018-10-06 VV556/HW3/submission.tex
ex1 ok

\section{Exercise3.1}

>>>>

\section{Exercise3.1}
	\begin{proof}
		Let $\phi(x) = (x^2 - 1)^n$, then
		\begin{equation}
			\phi(\pm 1) = \phi^{(1)}(\pm 1) = \cdots = \phi^{(n-1)}(\pm 1) = 0
		\end{equation}
		The $L^2$ norm of $P_n(x)$ is
		\begin{equation}
			\begin{aligned}
				||P_n||_2  & = \sqrt{\int_{-1}^{1} P_n^2(x) dx}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 \int_{-1}^{1} [\phi^{(n)}(x)]^2 dx}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n \int_{-1}^{1} \phi^{(2n)}(x) \phi(x) dx} \quad \text{(Integrate by parts)}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \int_{-1}^{1} (x^2 - 1)^n dx}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} (sin^2(x) - 1)^n cos(x) dx}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx}\\
			\end{aligned}
		\end{equation}
		Since
		\begin{equation}
			\int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx = \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times (2n+1)} 
		\end{equation}
		substitute it into the norm equation of $P_n$ yields
		\begin{equation}
			||P_n||_2 = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \cdot \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times(2n+1)}} = \sqrt{\frac{2}{2n+1}}
		\end{equation}
	\end{proof}
